---
title: "My Report as Vignette.rmd"
output:
  #rmarkdown::html_vignette: default
    bookdown::html_document2:
      base_format: rmarkdown::html_vignette
      number_sections: no
      fig_caption: yes
bibliography: my-bib.bib
vignette: > 
  %\VignetteIndexEntry{my-report-as-vignette} 
  %\VignetteEngine{knitr::rmarkdown}  
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
      message = FALSE, 
      warning = FALSE, 
      fig.width = 8)
```

```{r, include = FALSE}
#library(carData)
#library(ggplot2)
```


```{r}
library(CompendiumPackage)
```

Loading the required files to get coordinates randomly from a dataset. 
```{r}
source('coordinate-extractor-function.R')
knitr::read_chunk('coordinate-extractor-function.R')
```

## Uses of the Manhattan and the Euclidean Distances 
There are lots of interesting uses of the Manhattan vs. the Euclidean Distances. 
@singh2013k document the use of these different distances in differing k-means clustering approaches. 
@malkauthekar2013analysis mention their interesting uses in different facial recognition methods. These approaches differ only slightly yet offer a lot of insight into many algorithms in use today. 

A plot showing Euclidean distance between two points is shown in \@ref(fig:Euclidean)

## Demonstrating how to calculate the Euclidean distance between two points
The Euclidean distance is used in traditional mathematics to calculate the distance of two points. 

It involves calculating: 

    * The difference squared of the x coordinates of two points
    * The difference squared of the y coordinates of two points
    * Sum of the differences squared
    * Square root of the sum.

For example, the points (1,4) and (4,8) should evaluate to:

    * (4 - 1)^2 = 9 
    * (8 - 4)^2 = 16
    * 9 + 16 = 25
    * Euclidean Distance = square-root(25) = 5

Let us verify this with our function.
```{r}
euclidean_dist(x_1 = 1, x_2 = 4, y_1 = 4, y_2 = 8)
```
It works!

## Calculating the Manhattan Distance between the same two points.
The Manhattan distance is an untraditional distance measure. It can be thought off as taking the 'long way around' instead of following the hypotenuse like the Euclidean distance does. 

It involves calculating:

    * The absolute difference of the x coordinates of two points.
    * The absolute difference of the y coordinates of two points 
    * Sum of the absolute differences

For the sample example, the Manhattan Distance should evaluate to:

    * | 4 - 1 | = 3
    * | 8 - 4 | = 4
    * Manhattan Distance = 3 + 4  = 7 

Let us verify this with our function.
```{r}
manhattan_dist(x_1 = 1, x_2 = 4, y_1 = 4, y_2 = 8)
```
It works!

## Calculating the Manhattan and Euclidean Distances from random points
### Getting first random coordinate 
```{r}
# Generating one coordinate and extracting its x and y value 
set.seed(123)
coordinate_1 = get_coordinate_from_Burt()
coordinate_1
```
### Getting second random coordinate 
```{r}
set.seed(5)
coordinate_2 = get_coordinate_from_Burt()
coordinate_2
```
### Getting their Euclidean Distance 
```{r}
euclidean_dist(x_1 = coordinate_1[1], x_2 = coordinate_2[1], y_1 = coordinate_1[2], y_2 = coordinate_2[2])
```
### Getting their Manhattan Distance
Because the Manhattan distance is longer (i.e. the sum of two sides of a triangle rather than its hypotenuse), as a sanity check we expect it to be larger than 69. 
```{r}
manhattan_dist(x_1 = coordinate_1[1], x_2 = coordinate_2[1], y_1 = coordinate_1[2], y_2 = coordinate_2[2])
```
And we guessed right!

## Plotting the Euclidean Distance of the same coordinates as a straight line
```{r Euclidean, fig.cap = "\\label{fig:Euclidean}plotting example"}
plot_euclidean_dist(x_1 = coordinate_1[1], x_2 = coordinate_2[1], y_1 = coordinate_1[2], y_2 = coordinate_2[2])
```


